Fitness Cost

### 2021-11-08 graphs_newt_snakes/fitness_cost.Rmd
worked a bit more describing what I was doing for fitness cost

>>>>

I chose a phenotype of 3 to be half as good. This might be a tad too strong. To calculate cost I need to look at the fitness scaling (between 0 and 1) and make my chosen phenotype meet the line at half of the total fitness (0.5).

Fitness scaling = e^-cost

If a phenotype of 3 is half the total fitness the cost wold be log 2

c(p) = (a/b)^2
c(3) = (a/b)^2
log(2) = (a/b)^2
b = 3/log(2) = 10

SO cost = (phenotype/10)^2

**Special Note** Phenotype is arbitrary (scale for the snakes resistance)
